Final Project Data 205

### 2021-12-12 Draft Final Project1.Rmd
Add files via upload

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020","August-2020","May-2020","April-2020","March-2020","February-2020","January-2020","December-2019","November-2019","October-2019","June-2019","November-2018","March-2018","February-2018","January-2018","October-2017","September-2017")

url_exception_june_2020<-"https://www.wmata.com/about/transit-police/upload/June-2020-Blotter-Report.pdf"
df_exception_June_2020 <- get_wmata_data(url_exception_june_2020)

@@

```
## View df_wmata Data 
```{r}
view(df_wmata)
```

@@

## Create a New Column and Add Months and years to WMATA DataSet 
```{r}
mutate(date=as.Date(date,format="%Y"))
```

## Groupby Time Series( Define Time (Morning, DayTime, Night)

```{r}
#Create a time series 
```

@@

@@

## Remove Crimes Data 
```{r}
na.omit(crimes)
```

```{r}
view(crimes)
```

```{r}
names(crimes)[names(crimes) == 'Crime Name1'] <- 'Offenses'
```

```{r}
P1<-crimes %>%                        
  group_by(type) %>% 
  select("")
  summarize(n = n())
P1
```

```{r}
ggplot(crimes, aes(x=Offenses, fill=Offenses)) + 
  geom_bar( ) +
  scale_fill_hue(c = 40) +
  theme(legend.position="none")
```

>>>>

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020","August-2020","May-2020","April-2020","March-2020","February-2020","January-2020","December-2019","November-2019","October-2019","June-2019","November-2018","March-2018","February-2018","January-2018","October-2017","September-2017")
```

```{r}
url_exception_june_2020<-"https://www.wmata.com/about/transit-police/upload/June-2020-Blotter-Report.pdf"
df_exception_June_2020 <- get_wmata_data(url_exception_june_2020)

@@

## View df_wmata Data 
```{r}
view(df_wmata)
```

@@

## Separate year from date
```{r}
WMATA$date <- as.Date(WMATA$date, format="%m/%d/%Y")
head(WMATA)      
```

```{r}
WMATA$year<-as.numeric(format(WMATA$date,"%Y"))
head(WMATA)
```

## Groupby Time Series( Define Time (Morning, Afternoon ,Evening, Night)

```{r}
#Create a time series plot
WMATA$hour <- as.numeric(gsub(":.*$", "", WMATA$time))
WMATA$cat <- with(WMATA,  ifelse(hour >= 5 & hour<=11, "morning",
                            ifelse(hour>11 & hour<=16, "evening", "night")))
WMATA
```

@@

##Prepare the Data
```{r}
DMV<-WMATA %>%
  select(type,year)%>%
  filter(year >=2017  & type %in% c("ARREST","REPORT","SUMMONS/CITATION"))%>%
  group_by(year)
```

```{r}
head(DMV)
```

## Getting the WMATA Geocodes
```{r}
library(dplyr)
library(stringr)
library(tidygeocoder)

# Extract the street address from desc using Regex.  Extract crime description also.
df_wmata2 <- df_wmata %>% mutate(street_addr=str_remove(desc, "[[:upper:]]{2,}.+")) %>%
  mutate(crime_desc=str_extract(desc, "[[:upper:]]{2,}.+"))
df_wmata2 <- df_wmata2 %>% mutate(full_addr=paste(street_addr,state))

#Filter on just Maryland addresses
df_md <- df_wmata2 %>% filter(state=="MD")

#Apply the geocode function to get lat/lon values
coordinates <- df_md %>% geocode(full_addr)
```

```{r}
P5<- ggplot(DMV, aes(y =year, fill = factor(type))) +
  geom_boxplot() +
  facet_wrap(~type, scale = "free") +
  scale_y_continuous(name = "Average Life Expectancy") +
  scale_x_discrete(labels = abbreviate, name = "Continent")

P5
```

```{r}
ggplot(DMV, aes(x=type)) + geom_histogram()
```

```{r}
ggplot(diamonds, aes(x=price, y=color, fill=color)) +
```

```{r}
p <- ggplot(DMV, aes(year, type)) + 
  geom_abline() +
  geom_jitter(width = 0.1, height = 0.1) 
p + facet_wrap()
```

## Facet_wrap on the types of reports throughout the years
```{r}
ggplot(data = WMATA, aes(year, n)) +
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue") + 
  labs(title = "New Marvel characters by alignment",
       subtitle = "(limited to characters with more than 100 appearances)",
       y = "Count of new characters", x = "") + 
  facet_grid(~type==c("DC","MD","VA"))
```

@@

## Create on plot on Income & Population(Linear Regression/ Scatterplot with Population)
```{r}

## Remove Crimes Data 
```{r}
Moco_crimes<-na.omit(crimes)
```

## Plot on Classifcation of Crime
```{r}
c1<-crimes  %>%
  filter(`Crime Name1` %in% c("Crime Against Person","Crime Against Property","Crime Against Society")) %>%
  ggplot(aes(x=`Crime Name1`, fill=`Crime Name1`))+
  geom_bar()+
  labs(title="Classification of Crime",x="", y="Total")+
  scale_fill_brewer(palette = "Accent") + theme_minimal()
c1 + theme_minimal()
```

## 
```{r}
